Modelling the City of Melbourne Pedestrian Data

### 2017-09-30 presentation/final.Rmd
started slides of imputation evaluation: not sure if should be incldued

@@

@@

- general code which will run the algorithm
- inputs required: 
  * data in wide format
  * threshold value for missing values proportion (_default:_ `threshold = 0.1`)
  * max length of repeated values (_default:_ `maxlength = 17`)
- use R and RStudio with packages:
  * `dplyr`, `lubridate` and `tidyr` for data manipulation
  * `foreach` and `doSNOW` for parallel computing
  * `rwalkr` for accessing latest data
---
## Imputation Model Evaluation

@@

>>>>

neighbours <- list()

@@

  neighbours[[i]] <- closest_sensor

@@

- general code which will run the algorithm
- inputs required: 
  * data in wide format
  * threshold value for missing values proportion (_default:_ `threshold = 0.1`)
  * max length of repeated values (_default:_ `maxlength = 17`)
- use R and RStudio with packages:
  * `dplyr`, `lubridate` and `tidyr` for data manipulation
  * `foreach` and `doSNOW` for parallel computing
  * `rwalkr` for accessing latest data
---
## Imputation Model Evaluation
### In-sample Fit

@@

```{r}
MARE_glm_tr <- numeric()
for (i in unique(ped_data$Sensor)){
  MARE_glm_tr[i] <- mean(abs(fitted_data[[i]] - unlist(dfa[, i])), na.rm = T) / mean(unlist(dfa[, i]), na.rm = T)
}
```

---
class: center, middle
## Imputation Model Evaluation
### Out-of-sample cross validation
```{r, echo = FALSE}
test_fit <- list()
test_df <- original_df %>% filter(Date_Time > "2016-12-31")
  for(i in small_miss_sensors){
    test_fit[[i]] <- predict.glm(models[[i]],
                                 newdata = test_df,
                                 type = "response")
    }

  for(i in large_miss_sensors){
    ts_data <- data.frame(close_dfsc = (test_df[, neighbours[[i]][1]] %>% scale),
                          close_dfsc2 = (test_df[, neighbours[[i]][2]] %>% scale),
                          Time = test_df$Time)
    colnames(ts_data) <- c("close_df_scale", "close_df_scale2", "Time")
    test_fit[[i]] <- predict.glm(models[[i]],
                                 newdata = ts_data,
                                 type = "response")
  }
MARE_glm_ts <- numeric()
  for (i in unique(ped_data$Sensor)){
    MARE_glm_ts[i] <- mean(abs(test_fit[[i]] - unlist(test_df[, i])),
                           na.rm = T) / mean(unlist(test_df[, i]), na.rm = T)
    }

```{r, echo = FALSE, fig.retina = 6, message=FALSE, warning=F, fig.width = 3.5, fig.height = 3.5}
ggplot(test_df, aes(x = `Bourke Street Mall (North)`,
                    y = test_fit$`Bourke Street Mall (North)`)) +
                  geom_point(alpha = 0.5) +
                  scale_x_continuous(limits = c(0, 5000)) +
                  scale_y_continuous(limits = c(0, 5000)) +
                  xlab("Actual") + ylab("Fitted") + theme(aspect.ratio = 1) +
                  geom_abline(aes(slope = 1, intercept = 0),
                              colour = viridis(3)[1],
                              alpha = 0.7, size = 1.5,
                              linetype = 2) +
                  geom_smooth(method = "lm", size = 1.5, 
                       colour = viridis(3)[3]) +
                  ggtitle("Actual vs Fitted \n at Bourke Street Mall (North) in 2017")

```{r, echo = FALSE, fig.retina = 6, message=FALSE, warning=F, fig.width = 10, fig.height = 3}
fit_t_plot <- data.frame(fit = test_fit$`Bourke Street Mall (North)`,
                         Date_Time = test_df$Date_Time)  
ggplot(test_df %>% filter(Date_Time > "2017-08-31")) +
  geom_line(aes(x = Date_Time,
                y = fit), data = (fit_t_plot %>%
                                  filter(Date_Time > "2017-08-31")),
            colour = magma(3)[2], alpha = 0.6) +
  geom_line(aes(x = Date_Time,
                y = `Bourke Street Mall (North)`),
            alpha = 0.6) +
  scale_y_continuous(limits = c(0, 5000)) +
  theme_minimal() + xlab("Time") + ylab("Count") +
  ggtitle("Bourke Street Mall (North)")
